---
output: pdf_document
---
#Statistical Inference Assessment Part 1

##Question 1 
Firstly creating 1000 simulations of 40 exponential(0.2)s, and taking their corresponding means,
```{r}
NoOfExponentials<-40
NoOfSamples<-1000
lambda = 0.2
SimulatedResults<-apply(matrix(rexp(NoOfExponentials*NoOfSamples, lambda),NoOfSamples,NoOfExponentials),1,mean)
```
and distribution is centered at,
```{r}
mean(SimulatedResults)
```
and theoretical center of the distribution,
```{r}
1/lambda
```
So, they are quite close to each other.
    
##Question 2
Variance of the distribution is,
```{r}
var(SimulatedResults)
```
and theoretical variance is,
```{r}
((1/lambda)/sqrt(40))^2
```
So, they are quite close to each other. 
    
##Question 3
By looking at distribution, we easily infer that it is normal distribution.
```{r}
hist(SimulatedResults, # histogram
     col = "peachpuff", # column color
     border = "black", 
     prob = TRUE, # show densities instead of frequencies
     xlab = "Simulated Exponentials Mean",
     main = "Distribution of averages of 40 exponential(0.2)s",
     breaks = 60)
lines(density(SimulatedResults),lwd = 2, col = "chocolate3")
abline(v = mean(SimulatedResults),col = "royalblue",lwd = 2)
abline(v = median(SimulatedResults),col = "red",lwd = 2)
legend(x = "topright",c("Density plot", "Mean", "Median"),col = c("chocolate3", "royalblue", "red"),lwd = c(2, 2, 2))
```
    
##Question 4
The coverage of the confidence interval for 1/lambda: X¯±1.96*S/???n.
```{r}
mean(SimulatedResults) + c(-1,1)*1.96*sd(SimulatedResults)/sqrt(1000)
```