---
output: pdf_document
---
#Statistical Inference Assessment Part 2
   
##Question 1
I loaded the ToothGrowth data and perform some basic exploratory data analyses, 
```{r,fig.height=3}
library(lattice)
data(ToothGrowth)
xyplot(len~dose|supp,data=ToothGrowth,layout=c(2,1))
```

##Question 2
A basic summary of the data,
```{r}
str(ToothGrowth)
```
   
##Question 3
Firstly I tested the hypothesis that response of the length of odontoblasts (teeth) in each of 10 guinea pigs is high in case of "VC" as compared to "OJ"
```{r}
#First Hyp., that "VC" has good impact rather than OJ
t.test(ToothGrowth[ToothGrowth$supp=="OJ",]$len-ToothGrowth[ToothGrowth$supp=="VC",]$len)

```
then, I tested the hypothesis that response of the length of odontoblasts (teeth) in each of 10 guinea pigs is high as dose increases. So firstly I tested dose 0.5 with 1, later I tested dose 1 with 2,

```{r}
#Secon Hyp., that increased dose has good impact.
comp1<-subset(ToothGrowth,dose%in%c(0.5,1))
t.test(len~supp,data=comp1,paired = T)

comp2<-subset(ToothGrowth,dose%in%c(1,2))
t.test(len~supp,data=comp2,paired = T)
```
   
##Question 4
By looking at the above results, it seems that the response of the length of odontoblasts (teeth) in each of 10 guinea pigs at each of three dose levels of Vitamin C (0.5, 1, and 2 mg) is highly correlated. Higher the dose is, higher is the response of the length of teeths. But that response is quite independent of delivery methods (orange juice or ascorbic acid).